\tb{Place of Residence and Political Attitudes in Democracies Worldwide }

### 2018-12-03 Final Paper/PaperJLin.tex
Modified Table Orientations
Added analyses by region for Ideology as DV

\begin{figure}[ht!]    \centering
	{	 \includegraphics[width=\textwidth]{RegimeDemocracy}}
	\caption{\tb{Level of Democracy and Regime Age}}\label{figure2}
\end{figure}

@@

\begin{quote}
	\e {Hypothesis 1 -- Place Matters:} An individual's place of residence influences their political ideology such that the more distant the characteristics of one's vicinity gets from an urban city, the more conservative one will become.
\end{quote}

@@

In the \e{Issue Stances} hypothesis, I predict that people will understand the meaning of issues differently based on where they live and hold different opinions about them as a result of their place of residence. In other words, if the \e{place Matters} hypothesis holds true, people who live in rural areas will see issues differently than those who live in urban areas and apply their political ideologies when deciding on the issues.

Both the \e{Place Matters} and \e{Issue Stances} hypotheses assumes that countries are the same across the board and that one's conceptualization of place of residence is uniform. Therefore, in the last hypothesis, I will integrate some polity defining factors into the model to understand how certain aspects of each regime such as their level of democracy, regime age and electoral formula influence the relationships that are observed in the preceding hypotheses.

@@

Finally, I include the electoral formula as a means of understanding how the system of representation influences the relationship between the core variables used in this paper. A regime's electoral formula is the way in which citizens select their representatives and the mechanisms in which votes are tallied. It is unclear whether the electoral formula influences political discourse and attitude formation. however, past research suggests that this factor does not matter in the ways that place of residence will influence a person's political preference \cite{barkan_space_2006}. For the \e{Electoral Formula} hypothesis, I hypothesize that if individuals had to fight for representation in a winner take all system, personal factors such as place of residence will be more salient than if all interests were more fairly represented in a proportional system. Each of these components are then tied together to understand how idiosyncrasies of a polity lead to the difference between place of residence and political ideology as explored in the \e{Place Matters} and the \e{Issue Stances} hypotheses.

@@

The first regression will consider the core of the \e{Place Matters} hypothesis. I will regress the place of residence variable on the respondent's self-placement on the political ideology scale. The second, third and fourth regressions will factor in the effects of a country's level of democracy, regime age, and electoral formula at the time of the election into the picture to observe their influences on the relationship in the \e{Place Matters} hypothesis. A fifth regression will be employed to understand how the inclusion of all the variables influences the first hypothesis. These subsequent hypotheses are aimed at testing the components of Hypothesis 3.

@@

\subsubsection{\e{Place Matters} on the Worldwide Scale}

@@

\subsubsection{\e{Place Matters} By Geographic Region}

@@

@@

\begin{singlespace}
	\begin{table}[H]
		\centering
		%\def\arraystretch{1.5}
		\caption{\tb{Self-Placement Ideology - Scandinavia}}
		\begin{tabulary}{\linewidth}{l c c c}
			\\
			\hline
			\tb{Place of Residence}&\tb{Finland}&\tb{Iceland}&\tb{Sweden} \\
			\hline
			Small Town&.2546&1.131***&-.0247 \\
			&(.4143)&(.4036)&(.4636) \\
			Suburban&.0600&1.866***&.0325 \\
			&(.3463)&(.4081)&(.4431) \\
			Urban&-.6608&.9035**& .0217\\
			&(.4514)&(.3993)&(.4006) \\
			Constant&6.5998***&6.063***&2.352** \\
			&(1.123)&(.8182)&(1.116) \\
			N&187&428&330\\
			$R^2$&0.2158&0.1688&0.0677 \\
			\hline
		\end{tabulary}
		\\
		\e{Notes:} *p$<$.1, **p$<$.05. ***p$<$.01 \\
		\e{Reference:} A rural place of residence serves as the baseline for comparison
		\label{table6}
	\end{table}
\end{singlespace}

\begin{singlespace}
	\begin{table}[H]
		\centering
		%\def\arraystretch{1.5}
		\caption{\tb{Self-Placement Ideology - Central Europe}}
		\begin{tabulary}{\linewidth}{l c c c c}
			\\
			\hline
			\tb{Place of Residence} &\tb{Austria}&\tb{Czech Republic}& \tb{Poland} &\tb{Slovakia} \\
			\hline
			Small Town&.6270**& -.1272 & .3032 & .3954  \\
			&(.3139) & (.2920) & (.2002) & (.3216) \\
			Suburban&-.0326& -.4467&.0666 & 2.1723\\
			&(.3343)&(.4993) & (.3104) & (.1.107)\\
			Urban&.3822&.5199 & .0954 & 1.1440 \\
			&(.3888) &(.2944) & (.2662) & (.4518) \\
			Constant& 4.014***& 3.930***& 5.096*** & 4.3473***  \\
			&(.9272) & (.8696) & (.8646) & (1.127) \\
			N&247& 511& 895 & 392 \\
			$R^2$&0.1126&0.2538 & 0.1348 & 0.1498 \\
			\hline
		\end{tabulary}
		\\
		\e{Notes:} *p$<$.1, **p$<$.05. ***p$<$.01 \\
		\e{Reference:} A rural place of residence serves as the baseline for comparison
		\label{table7}
	\end{table}
\end{singlespace}

@@

@@

@@

@@

@@

\begin{landscape}
	\begin{table}
		\centering
		\def\arraystretch{1.5}
		\caption{\tb{Self-Placement Ideology - Pacific Islands}}
		\begin{tabulary}{\linewidth}{l c c }
			\\
			\hline
			\tb{Place of Residence}&\tb{New Zealand (2011)}&\tb{Philippines}\\
			\hline
			Small Town & -.3603  & .6010  \\      
			& (.3050) & (.8141)    \\
			Suburban  & -   & .7878  \\ 
			 & -   & (1.4391)       \\
			Urban  & -.0154   & .3447 \\
			 &(.2926)   & (.4770)      \\
			Constant  & 5.176***  & 7.838***   \\
			&(.8503)&(1.8952) \\
			N  &586 & 115  \\
			$R^2$  &0.0491  &0.0627     \\
			\hline                                       
		\end{tabulary} 
		\\
		\e{Notes:} *p$<$.1, **p$<$.05. ***p$<$.01 \\
		\e{Reference:} A rural place of residence serves as the baseline for comparison
		\label{table13}
	\end{table}
\end{landscape}

@@

@@

The goal of this paper is not to make generalizations about how people who live in suburbia around the world compare to those in the rural countryside when it comes to political attitudes, rather, it is to gain a general understanding of how the variables of place and political attitudes relate on a broad and specific level. From the data, I can draw the following conclusions. First, place matters. In the \e{Place Matters} hypothesis, the results confirm the findings such that urban residents, on average, differ from their rural counterparts when it comes to political ideology. The results confirm that urban residents, along with small town and suburban residents, tend to be more left leaning than their rural counterparts. However, the average difference between urban and rural, suburban and rural, and even small town and rural, are not necessarily increasing as one moves towards the city. Residents of the global suburbia, on average, see themselves to be more left leaning than their urban counterparts.

Second, the \e{Issue Stances} hypothesis is supported by the data because a person's place of residence does influence how one conceptualizes the issues and rate their support. However, as seen in Table \ref{table14}, urban residents are, on average, more conservative on their willingness to spend public dollars than their rural counterparts. This comes in contrast with the results in the \e{Place Matters} hypothesis. While urban residents may see themselves as more left leaning, they may have other motivations to limit their support for social and economic policy.

@@

\section{\e{Place Matters} - General Trends}
\label{AppendixD}

>>>>

\begin{figure}[ht!]    \centering
	{	 \includegraphics[width=\textwidth]{AgeDemPF}}
	\caption{\tb{Level of Democracy and Regime Age}}\label{figure2}
\end{figure}

@@

\begin{quote}
	\e {Hypothesis 1 -- Self-Identified Ideology:} An individual's place of residence influences their political ideology such that the more distant the characteristics of one's vicinity gets from an urban city, the more conservative one will become.
\end{quote}

@@

In the \e{Issue Stances} hypothesis, I predict that people will understand the meaning of issues differently based on where they live and hold different opinions about them as a result of their place of residence. In other words, if the \e{Self-Identified Ideology} hypothesis holds true, people who live in rural areas will see issues differently than those who live in urban areas and apply their political ideologies when deciding on the issues.

Both the \e{Self-Identified Ideology} and \e{Issue Stances} hypotheses assumes that countries are the same across the board and that one's conceptualization of place of residence is uniform. Therefore, in the last hypothesis, I will integrate some polity defining factors into the model to understand how certain aspects of each regime such as their level of democracy, regime age and electoral formula influence the relationships that are observed in the preceding hypotheses.

@@

Finally, I include the electoral formula as a means of understanding how the system of representation influences the relationship between the core variables used in this paper. A regime's electoral formula is the way in which citizens select their representatives and the mechanisms in which votes are tallied. It is unclear whether the electoral formula influences political discourse and attitude formation. however, past research suggests that this factor does not matter in the ways that place of residence will influence a person's political preference \cite{barkan_space_2006}. For the \e{Electoral Formula} hypothesis, I hypothesize that if individuals had to fight for representation in a winner take all system, personal factors such as place of residence will be more salient than if all interests were more fairly represented in a proportional system. Each of these components are then tied together to understand how idiosyncrasies of a polity lead to the difference between place of residence and political ideology as explored in the \e{Self-Identified Ideology} and the \e{Issue Stances} hypotheses.

@@

The first regression will consider the core of the \e{Self-Identified Ideology} hypothesis. I will regress the place of residence variable on the respondent's self-placement on the political ideology scale. The second, third and fourth regressions will factor in the effects of a country's level of democracy, regime age, and electoral formula at the time of the election into the picture to observe their influences on the relationship in the \e{Self-Identified Ideology} hypothesis. A fifth regression will be employed to understand how the inclusion of all the variables influences the first hypothesis. These subsequent hypotheses are aimed at testing the components of Hypothesis 3.

@@

\subsubsection{\e{Self-Identified Ideology} on the Worldwide Scale}

For the first model, a regression was conducted to see if there is a general trend between place and self-placement on a 10-point ideology scale. Furthermore, the regression was conducted separately for each election that was represented in this dataset. Table \ref{table3} shows the results for this regression on the global scale. This general trend suggests that, without considerations of any polity-specific factors, there is a difference between the global rural residents, small town and suburban residents in terms of their political ideologies. The trends described in this table suggests that, on a general level, there lies a difference between where people live and their political attitudes. However, several caveats are present in this analysis. From here, we are assuming that individuals conceptualize the places of residence in a similar fashion across geographic boundaries. Additionally, this analysis does not take into account country-specific measures such as the presence of the different possibilities of residence for the people. As I noted in Table \ref{table2}, not all the countries have respondents from each place of residence as categorized in the CSES. Therefore, it would help to break down the analysis by country.

@@

The trends presented in this table suggest an interesting deviation from the \e{Self-Identified Ideology} Hypothesis, and from patterns observed in the United States and Canada, described in the literature review. Here, urban residents are around a quarter of a point more conservative than their rural counterparts. This trend emphasize the need to break down the analysis by country to understand how specific factors within the regions and political boundaries shape these trends.

\subsubsection{\e{Self-Identified Ideology} By Geographic Region}

When the analysis is broken down by the countries themselves, we see a clearer patterns between place of residence and political attitudes of the respondents to the CSES survey. Each country is displayed and analyzed with their regional neighbors. Additionally, these trends are discussed in context of some key macro variables present for each polity that is displayed in Figure \ref{figure2} and Appendix \ref{AppendixC}. By conducting the analyses in this manner, we can also see if there is a neighborhood effect, such that countries that are located near one another are similar in democratic and demographic ideological arenas.

@@

Central America (as represented by Mexico in the 2012 and 2015 elections) and Latin American (represented by Peru) show some distinct patterns when it comes to the relationship of place and political ideology. Table \ref{table4} shows the results of the analysis. Both countries are relatively similar in their regime age, with Mexico being a democracy for 18 years at 2015 and Peru at 15 years in their 2016 election. Despite slightly different levels of democracy and distinct electoral formulas, both countries are relatively similar in their urban-rural trends. Both Mexico in 2012 and Peru show urban residents as more right leaning than their rural counterparts. Despite a relatively high coefficient, the difference is not statistically significant. However, Mexico in 2015 shows that urban residents are a point more to the left than their rural counterparts with statistical significance. This point difference is relatively large on a 10-point scale. For this region, we do not necessarily see regional similarities as only one polity (Mexico in 2015) supports the \e{Self-Identified Ideology} Hypothesis.

@@

In Western Europe, the results confirm the \e{Self-Identified Ideology} hypothesis for France, but not Germand. In Table \ref{table5}, we can see that differences between France and Germany lie in the distinction between urban residents compared to rural residents. While both countries see urban residents lean left on the self-identified scale, France is more statistically significant in their .64 point jump to the left, which is relatively large for a 10 point scale. Geographically, Germany is considered more in Central Europe; however, their political activity makes them a worthwhile comparison to Western Europe.

\begin{singlespace}
	\begin{table}[H]
		\centering
		%\def\arraystretch{1.5}
		\caption{\tb{Self-Placement Ideology - Central Europe}}
		\begin{tabulary}{\linewidth}{l c c c c}
			\\
			\hline
			\tb{Place of Residence} &\tb{Austria}&\tb{Czech Republic}& \tb{Poland} &\tb{Slovakia} \\
			\hline
			Small Town&.6270**& -.1272 & .3032 & .3954  \\
			&(.3139) & (.2920) & (.2002) & (.3216) \\
			Suburban&-.0326& -.4467&.0666 & 2.1723\\
			&(.3343)&(.4993) & (.3104) & (.1.107)\\
			Urban&.3822&.5199 & .0954 & 1.1440 \\
			&(.3888) &(.2944) & (.2662) & (.4518) \\
			Constant& 4.014***& 3.930***& 5.096*** & 4.3473***  \\
			&(.9272) & (.8696) & (.8646) & (1.127) \\
			N&247& 511& 895 & 392 \\
			$R^2$&0.1126&0.2538 & 0.1348 & 0.1498 \\
			\hline
		\end{tabulary}
		\\
		\e{Notes:} *p$<$.1, **p$<$.05. ***p$<$.01 \\
		\e{Reference:} A rural place of residence serves as the baseline for comparison
		\label{table6}
	\end{table}
\end{singlespace}

However, when placed in the context of the Central European states, Germany does fit in well with Austria, Czech Republic, Poland and Slovakia in terms of the rural-urban divide. All countries in this region are roughly 20-24 years of age, with a median of 23 years. Here, the regimes are all relatively free in terms of their level of democracy. With the exception of Germany, all regimes here are proportional systems. None of these countries show statistical significance when it comes to political ideologies in the form of self-identification. While many of the values are relatively large, there are good chances that these observations can be from chance alone.

\begin{singlespace}
	\begin{table}[H]
		\centering
		%\def\arraystretch{1.5}
		\caption{\tb{Self-Placement Ideology - Scandinavia}}
		\begin{tabulary}{\linewidth}{l c c c}
			\\
			\hline
			\tb{Place of Residence}&\tb{Finland}&\tb{Iceland}&\tb{Sweden} \\
			\hline
			Small Town&.2546&1.131***&-.0247 \\
			&(.4143)&(.4036)&(.4636) \\
			Suburban&.0600&1.866***&.0325 \\
			&(.3463)&(.4081)&(.4431) \\
			Urban&-.6608&.9035**& .0217\\
			&(.4514)&(.3993)&(.4006) \\
			Constant&6.5998***&6.063***&2.352** \\
			&(1.123)&(.8182)&(1.116) \\
			N&187&428&330\\
			$R^2$&0.2158&0.1688&0.0677 \\
			\hline
		\end{tabulary}
		\\
		\e{Notes:} *p$<$.1, **p$<$.05. ***p$<$.01 \\
		\e{Reference:} A rural place of residence serves as the baseline for comparison
		\label{table7}
	\end{table}
\end{singlespace}

Looking to the north, countries in the Scandinavian region are said to be some of the most free in Europe and also have relatively old democracies. As shown in Table \ref{table7}, the only country that shows significance in the urban-rural divide is Iceland, but it is nearly a full point to the right. Despite the statistical significance, this proves to be an interesting deviation from the \e{Self-Identified Ideology} hypothesis.

@@

In Southwestern Europe, the results in Table \ref{table8} suggest an interesting set of results. For both Greece and Romania, the countries are represented by two elections and both are in a position where the former election suggests significance in place but not the latter. In Greece, the 2012 election respondents are more likely to lean left when living in an urban place of residence, which supports the \e{Self-Identified Ideology} hypothesis. However, this pattern is the opposite in Romania, where the 2012 respondents showed that urban residence led to more right-leaning political ideologies. The effect of place is not statistically significant in any other country in this region.

@@

In Eastern Europe, Table \ref{table9} shows the results for Latvia's 2011 and 2014 elections and the results do not reflect patterns of influence with regards to place and ideology. With the consideration of the regime age, level of democracy and electoral formula, Latvia shares similar trends with states in Central and Southwestern Europe, which suggests that these macro-trends may play a role in explaining macro trends in the relationship between place of residence and an individual's political ideology.

@@

The Middle East provides an interesting set of countries since it exemplifies the one of the most free (Israel) and least free (Turkey) countries represented in this CSES dataset. These countries are both proportional in its electoral formula but differ by regime age. Yet, despite these differences, both countries do not show a place divide in political ideology. While Israel does not have an "urban center" due to the way place is defined in Israel, there are no signs of differences between any of the other areas and the rural settlements of the state.

@@

Africa was originally represented by both Kenya and South Africa. However, with the introduction of controls, the lack of response in one of the areas led to the isolation of South Africa as the sole state in Africa for this analysis. The continent of Africa is one of the most recent places to transition to democracy in the wake of the decolonization movements. However, despite being a democracy for only 20 years, South Africa shows that there are differences between their urban and rural residents with their urban residents rating themselves a full point to the left. It is important to note that place of residence was not directly asked of the participants during the data collection. It is a code used by the researchers for identification purposes. Nonetheless, the results in Table \ref{table11} suggest that there is a significant difference between residents in rural and urban places in a recently transitioned regime in Afrtica, a trend that is not seen in their Central and Eastern European counterparts that share a regime age and level of democracy.

@@

Table \ref{table12} show the patterns in Asia represented by Japan and South Korea. Both countries utilize the mixed electoral formula. Japan is older than South Korea as a regime and also more free. Respondents to the Japan study showed difference in place of residence when it comes to political ideology. The residents of Japan's urban centers (cities more than 200,000 people) tend to be more conservative by close to two-thirds of a point on the 10-point ideology scale. The move to the right is gradually seen through the responses of the small town and suburban residents of Japan as well. In South Korea, suburban residents are two and a quarter points to the left of their rural counterparts, suggesting that the \e{Self-Identified Ideology} phenomena happens in the suburbs of South Korea than in the urban centers.

Regionally speaking, the Philippines are often considered to be part of Asia given the ethnic identities of the people, however, their geographic location can also qualify them to be a pacific island. Therefore, while Table \ref{table13} shows the trends of the Philippines and New Zealand, I will analyze them in the broader context of Asia. The Philippines is a relatively young democracy and has a rating of 8 on the level of democracy scale. New Zealand has one of the most free in the region (similar to Japan) and is also the oldest. Yet, none of these two countries show a place divide when it comes to political ideology. Therefore, in Asia as a whole, the presence of a rural-urban divide in some countries and not others suggest that there is not a regional influence not are there patterns between levels of democracy, regime age, and electoral formula that influence the relationship between place of residence and political ideology.

\begin{singlespace}
	\begin{table}[H]
		\centering
		%\def\arraystretch{1.5}
		\caption{\tb{Self-Placement Ideology - Pacific Islands}}
		\begin{tabulary}{\linewidth}{l c c }
			\\
			\hline
			\tb{Place of Residence}&\tb{New Zealand (2011)}&\tb{Philippines}\\
			\hline
			Small Town & -.3603  & .6010  \\      
			& (.3050) & (.8141)    \\
			Suburban  & -   & .7878  \\ 
			 & -   & (1.4391)       \\
			Urban  & -.0154   & .3447 \\
			 &(.2926)   & (.4770)      \\
			Constant  & 5.176***  & 7.838***   \\
			&(.8503)&(1.8952) \\
			N  &586 & 115  \\
			$R^2$  &0.0491  &0.0627     \\
			\hline                                       
		\end{tabulary} 
		\\
		\e{Notes:} *p$<$.1, **p$<$.05. ***p$<$.01 \\
		\e{Reference:} A rural place of residence serves as the baseline for comparison
		\label{table13}
	\end{table}
\end{singlespace}

@@

Throughout this analysis of regions and considerations of specific polities' political idiosyncrasies, we cannot discern a pattern that shows how place of residence influences how one places themselves on the ideological spectrum, nor can we discern a pattern from how macro variables such as regime age, level of democracy and electoral formula influences the effects that the variables have on each other. Additionally, with the exception of Central and Eastern Europe, there does not seem to be another region where the countries that are represented in this dataset have some form of discernible regional pattern.

In the next section, I turn to the influence of place using an objective measure of beliefs in political actions based on social and economic pollicy and spending. From here, we can see if there is a relationship between how individuals describe themselves and how their objective issue stances play out based on where they live.

@@

The goal of this paper is not to make generalizations about how people who live in suburbia around the world compare to those in the rural countryside when it comes to political attitudes, rather, it is to gain a general understanding of how the variables of place and political attitudes relate on a broad and specific level. From the data, I can draw the following conclusions. First, place matters. In the \e{Self-Identified Ideology} hypothesis, the results confirm the findings such that urban residents, on average, differ from their rural counterparts when it comes to political ideology. The results confirm that urban residents, along with small town and suburban residents, tend to be more left leaning than their rural counterparts. However, the average difference between urban and rural, suburban and rural, and even small town and rural, are not necessarily increasing as one moves towards the city. Residents of the global suburbia, on average, see themselves to be more left leaning than their urban counterparts.

Second, the \e{Issue Stances} hypothesis is supported by the data because a person's place of residence does influence how one conceptualizes the issues and rate their support. However, as seen in Table \ref{table14}, urban residents are, on average, more conservative on their willingness to spend public dollars than their rural counterparts. This comes in contrast with the results in the \e{Self-Identified Ideology} hypothesis. While urban residents may see themselves as more left leaning, they may have other motivations to limit their support for social and economic policy.

@@

\section{\e{Self-Identified Ideology} - General Trends}
\label{AppendixD}
